Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
k=2 Stefan's comments

\noindent
\textbf{Component-based algorithm.}
Now we describe the algorithm \TAlg that we use throughout this section.
The algorithm partitions nodes into components, and
initially, each node belongs to its own singleton component.
For each pair of nodes $\set{x,y}$, \TAlg maintains a counter $C_{\set{x,y}}$ and increments it on every external request between $x$ and $y$.
Once $C_{\set{x,y}} = \alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest component respecting partitioning.
If no such partitioning exists, \TAlg resets all components to singletons, resets all counters to $0$, and ends the phase.

@@

	If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the reconfiguration is local within $U$ and $V$.
	In this case, a local repartition is possible (within $U$ and $V$), for a cost of at most $2$ swaps.
	Note that it is impossible that either $U$ or $V$ is of type $C_3$, as otherwise, a components of size $3$ participates in a merge, which results in a component of size at least $4$, and in this case no component respecting partitioning exists, a contradiction.

@@

	Now we bound $\TAlg(\sigma_I)$.
	A~cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as $2$ of pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
	Other cluster types contribute less: $C_1$ contributes $0$ and $C_2$ contributes $\alpha$.
	Summing this over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

@@

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	Alg collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

@@

\section{Distributed Implementation}
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip

>>>>

\noindent
\textbf{Component-based algorithm.}
Now we describe the algorithm \TAlg.
The algorithm partitions nodes into components, and
initially, each node belongs to its own singleton component.
For each pair of nodes $\set{x,y}$, \TAlg maintains a counter $C_{\set{x,y}}$ and increments it on every external request between $x$ and $y$.
Once $C_{\set{x,y}} = \alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest component respecting partitioning.
If no such partitioning exists, \TAlg resets all components to singletons, resets all counters to $0$, and ends the phase.

@@

	If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the reconfiguration is local within $U$ and $V$.
	In this case, a local repartition is possible (within $U$ and $V$), for a cost of at most $2$ swaps.
	Note that it is impossible that either $U$ or $V$ is of type $C_3$, as otherwise, a components of size $3$ participates in a merge.
	After merge, we would have a component of size at least $4$, and in this case no component respecting partitioning exists, a contradiction.

@@

	Now we bound $\TAlg(\sigma_I)$.
	A~cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as two pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
	Other cluster types contribute less: $C_1$ contributes $0$ and $C_2$ contributes $\alpha$.
	Summing this over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

@@

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter.
	I.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

@@

\section{Discussion and Future Work}
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip
